What We Eval in the Shadows

### 2021-09-03 paper/main.tex
Fix typos and grammar in Section 7

\begin{tabular}{@{}p{.97\linewidth}}
\medskip\EE{$min(e)=\c{model.frame}$}\\[-2mm]\small The \k{model.frame} function
returns a dataframe resulting from fitting the model described in a formula.
This shape subsumes \k{F(F(X))}, \k{FUN}, and assignments. It is the single most
popular function invoked from \eval. Each call does a median of 2K instructions.
\end{tabular}

@@

In R, \eval is used chiefly for meta-programming and accessing remote
environments. Unlike JavaScript which had a small set of well-defined patterns
that could be rewritten without \eval, our results suggest that \eval is an
integral part of programming in R.

@@

\begin{lstlisting}[caption={Unnecessary use of \eval},label=lst:unnecessary]
 PerformanceAnalytics::chart.QQPlot <- function (d="norm",dp,...) {
   q.f <- eval(parse(text=paste0("q",d)))
   z <- NULL
   eval(parse(text=paste0("z<-q.f(",dp,",...)")))
\end{lstlisting}

@@

We have not yet touched on alternative implementations of \eval. The tidyverse
libraries\footnote{An opinionated collection of R packages designed for data
science. It consists of some of the most popular packages.} include their own
implementation calls \k{rlang::eval\_tidy}~\cite{tidyverse}. This departs from
\eval in two ways. First, it supports evaluation of quosures, custom objects
used for metaprogramming that bundle expressions with an environment.
\k{eval\_tidy} accepts a data mask argument, a set of bindings such as a
dataframe or list, which takes precedence over the environment. Effects such as
assignments happen in the data mask. Expressions such as \k{return()} do not
work since the data mask does not correspond to a frame on the call stack.

>>>>

\begin{tabular}{@{}p{.97\linewidth}}
\medskip\EE{$min(e)=\c{model.frame}$}\\[-2mm]\small The \k{model.frame} function
returns a data frame resulting from fitting the model described in a formula.
This shape subsumes \k{F(F(X))}, \k{FUN}, and assignments. It is the single most
popular function invoked from \eval. Each call does a median of 2K instructions.
\end{tabular}

@@

In R, \eval is used chiefly for meta-programming and accessing remote
environments. Unlike JavaScript, which according to ~\citet{ecoop11} had a small
set of well-defined patterns that could be rewritten without \eval, our results
suggest that \eval is an integral part of programming in R.

@@

\begin{lstlisting}[caption={Unnecessary use of \eval},label=lst:unnecessary]
 PerformanceAnalytics::chart.QQPlot <- function (d="norm",dp,...) {
   q.f <- eval(parse(text=paste0("q",d)))
   z <- NULL
   eval(parse(text=paste0("z<-q.f(",dp,",...)")))
\end{lstlisting}\medskip

@@

We have not yet touched on alternative implementations of \eval. The tidyverse
libraries\footnote{An opinionated collection of R packages designed for data
  science. It consists of some of the most popular packages.} include their own
implementation of \eval called \k{rlang::eval\_tidy}~\cite{tidyverse}, which
departs from \eval in two ways. First, it supports the evaluation of quosures,
custom objects used for metaprogramming that bundle expressions with an
environment. The \k{eval\_tidy} function accepts a data mask argument, a set of
bindings such as a data frame or list, which takes precedence over the
environment. Effects such as assignments happen in the data mask, and
expressions such as \k{return()} do not work since the data mask does not
correspond to a frame on the call stack.
